Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-01-07 paper.tex
Un par de chuminás
Ahora le meto caña. :D
Abstract e intro revisados
Comentarios con etiqueta 'Antonio'

%%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
\title{Predicting sales of newly published books}

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
\author {
P.A. Castillo, A.M. Mora, J.J. Merelo, P. Garc\'{\i}a-S\'anchez, \\ A.J. Fern\'andez-Ares, M.G. Arenas, P. de las Cuevas
}
\institute{Department of Architecture and Computer Technology. CITIC \\
           University of Granada (Spain) \\
~\\
           e-mail: {\tt pacv@ugr.es}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is published the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached shelves. 
In this paper, which works with several years of data on published books in
Spain, we first apply a data visualization and preprocessing strategy
in order to find
out what are the variables that have some impact on sales, and
then use standard data mining software to predict sales, and from them
deduce print-run, based on those variables. Our work focuses then in  discovering which
are the most relevant variables when predicting sales and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishers,
since the obtained models provide guidance on the decision process of
publishing a book and do not require human intervention either for the operation or for
interpretation.
\end{abstract}

%********************************************************************************
\section{Introduction}

Publishing a book, as releasing any other product, implies several
types of risks and costs due to
the complexity and expenses of the production and distribution processes. 
% tienes que enmarcar el problema. Se trata de productos culturales
% con soporte físico y con ventas relativamente pequeñas. Libros,
% discos, no sé si alguna cosa más. - JJ
A newly launched product is also new to the company, and sales forecasts can
only be based on the experience of similar products. 
In this scope, having accurate estimates of future sales of the new
product is extremely important \cite{ChingChin2010} so that production
runs do not exceed predicted sales. 
Indeed, several studies have demonstrated that improving sale predictions 
(a reduction of forecasting errors) results in an improvement in the 
production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

@@

Book publishers, as well as other content producers, release new {\em
  products} more frequently than other industries and thus face the
problem of predicting sales quite often. The issue, in this case, is to print an
adequate number of copies but not too many, as the unsold volumes will
lead to losses and sunk inventory cost, whereas if the number of printed copies was not
enough, you can always print more. In this sense, errors in one or the
other direction do not have the same importance, although a temporal
scarcity of a book that is selling well is also a problem.

Thus, it is extremely important using predictive tools to optimize 
production and improve the publishing company profits or minimize losses \cite{Zhao2001}
by forecasting the sales a new book might achieve. This is the
objective we have in this paper.
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. %publishing roll.  
% [Pedro] "publishing roll" es como he encontrado "tirada editorial" traducido...
% Antonio propone traducirlo como "print run". Lo pongo así.

However, accurately using a predictive tool is a difficult task as
book sales are influenced by various factors that make
them fluctuate and usually they might be not controllable and
sometimes unknown. 
Some have to do with decisions on purchases, others with freight %FERGU: El Some have to do me suena raro
traffic, and others with the distribution strategy \cite{Little1998}.

Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager can eventually 
take them into account \cite{Armstrong2001,SThomassey2014}. 
                                % ¿Esto también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ
                                % [Pedro] esto iba referido a la Industria Editorial.
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they do? What are the results?

In this research, the problem of how many books should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for libraries, 
publishers and distributors. 
Usually, the company's expert sales managers analyzed historical data 
and applied their knowledge using external variables to calculate
appropriate predictions, for example, increasing or decreasing the 
sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.
%In any case, in general companies usually use a forecasting model and then, 
%an expert applies his knowledge, as the company might require an 
%interpretable and understandable model. 
However, carrying out the analysis and forecasting process as described,
may lead to an imprecise analysis and may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is large, and even, different experts can reach different
predictions from the same data set \cite{ChingChin2010,Sanders1994}.

For these reasons, the industry requires the best suited forecasting
techniques to be adopted so that, estimating sales task is carried out
properly and in an automatic way.

With this in mind, in this paper a data visualization and preprocessing strategy 
to find out what are the relevant variables describing a book in the prediction 
of book sales is proposed; then several standard data mining models 
for sales forecasting are evaluated so a publishing company 
can deduce and optimize print-run.

The rest of this paper is structured as follows: next, 
Section \ref{sec:soa} presents a comprehensive review of the
approaches found in the bibliography related to the prediction of
sales from product characteristics. 
Then, Section \ref{sec:problem} describes the 
problem of how many books should be printed when a new book is published, 
        % no es el problema de publicación, es el problema de venta
        % de libros sin publicar. Habrá que buscar un nombre - JJ
        %[Pedro] cierto, lo cambio, aunque me ha quedado un nombre muy largo  :)
 followed by Section \ref{sec:methodology} where the
experimental setup and the methodology considered in the study is
presented.  %FERGU: mejor described para no repetir
Section \ref{sec:experiments} reports and analyzes the obtained results with a 
real data set. Finally, conclusions and future work are presented in Section
\ref{sec:conclusionsAndFutureWork}.

@@

The initial data set, provided in the framework of a contract by
Trevenque Editorial, included 3159 books, and included descriptive information 
for each book, such as price, points of sale, subject, publisher, sales, returns, 
among other information.
Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
each book.

\begin{table}[!h]
\caption{Parameters describing a book, as provided by the company Trevenque.}
\label{tabla:paramsOrig50}
\begin{center}
\begin{tabular}{|c|c|}
\hline

@@

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=stages.eps,width=7cm}
\caption{\small{Three main stages in a typical sales prediction process: data analysis, (2) forecasting 
methods testing, and (3) subjectively adjusting the obtained results.}}
\label{fig:stages}
\end{center}
\end{figure}

@@

 % weka.classifiers.functions.LinearRegression
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
 \item \emph{Linear Regression}:
 Linear regression \cite{Cohen2003,Yan2009,Rencher2102} method models the 
relationship between a scalar dependent variable (outcome) and several independent 
variables (predictor) over the range of values in the data set. 
In this statistical technique, data is modeled using linear functions to estimate 
unknown model parameters, examining the linear correlations between independent 
and dependent variables.

@@

Once the methods to be applied have been chosen, they must be applied to data sets 
to obtain the prediction models for each one. 
Later on, the models ability must be validated on non-previously seen data.
Specifically, instead of using the conventional validation strategy based on 
using a training set and later on a testing set (unknown data against which 
the model must be tested), a cross-validation technique \cite{Geisser1993,Kohavi1995,Devijver1982} 
has been used to estimate how accurately the predictive model will perform in 
practice. %, limiting at the same time the overfitting problem.

@@

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	      & MAE 		& RMSE 		& RAE (\%) & RRSE (\%) 		\\
\hline
  M5P 		& 24.24 $\pm$ 0.96    & 197.48  & 577.28  & 35.21    & 41.85  \\
\hline
  LR 		  & 3533.84 $\pm$ 178.38& 247.22 & 561.67  & 44.08    & 40.71    \\
\hline
  SVM 		& 5586.96 $\pm$ 139.71& 215.69  & 574.76  & 38.46    & 41.66  \\
\hline
  kNN 		& 0.02 $\pm$ 0.00     & 302.07 	& 924.94 	& 53.86 	 & 67.05 	\\
\hline
  MLP 		& - 	  & - 	& - 	& - 	& - 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the original dataset (16 variables per book). 
    In this case, due to the categorial variables, the MLP could not be run.}} 
\label{tabla:resultsT}
\end{table*}

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 7 variables per book (obtained 
using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
%In this dataset, every book is described using numerical variables, and thus, 
%processing the data to build the different models is a fast task.
%***************************************
% TODO: falta rellenar la tabla, una vez que hagamos el análisis con el SOM y decidamos qué variables incluir en este dataset
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & 1.74 $\pm$ 0.10     & 218.81  & 661.85  & 39.01    & 47.98  \\
\hline
  LR      & 0.27 $\pm$ 0.02     & 258.82  & 582.74  & 46.15    & 42.24  \\
\hline
  SVM     & 45.58 $\pm$ 1.89    & 240.18  & 614.30  & 42.82    & 44.53  \\
\hline
  kNN     & 0.04 $\pm$ 0.00     & 221.21  & 520.17  & 39.44    & 37.71  \\
\hline
  MLP     & 8.99 $\pm$ 0.10   & 353.70 $\pm$ 57.74 & 624.87 $\pm$ 86.77  & 63.06 $\pm$ 10.29  & 45.30 $\pm$ 6.29   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained after the SOM analysis (7 variables per book).}}
\label{tabla:resultsSOM}
\end{table*}

@@

\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & 2.27 $\pm$ 0.02     & 195.97  & 629.33  & 34.94    & 45.62  \\
\hline
  LR      & 0.38 $\pm$ 0.01     & 256.19  & 549.19  & 45.68    & 39.81   \\
\hline
  SVM     & 132.64 $\pm$ 2.86   & 230.66  & 613.27  & 41.12    & 44.45   \\
\hline
  kNN     & 0.06 $\pm$ 0.01     & 214.76  & 551.33  & 38.29    & 39.96   \\
\hline
  MLP     & 130.77 $\pm$ 1.51   & 326.60 $\pm$ 75.77 & 687.61 $\pm$ 55.70  & 58.23 $\pm$ 13.51  & 49.84 $\pm$ 4.04   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained using the ReliefFAttributeEval 
feature selection method (8 variables per book).}}
\label{tabla:results9}
\end{table*}

@@

\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 2.02 $\pm$ 0.01     & 205.52  & 556.90  & 36.64     & 40.37  \\
\hline
  LR      & 0.32 $\pm$ 0.00     & 261.04  & 547.42  & 46.54     & 39.68   \\
\hline
  SVM     & 81.74 $\pm$ 1.66    & 242.26  & 606.07   & 43.19    & 43.93   \\
\hline
  kNN     & 0.05 $\pm$ 0.00     & 216.05  & 506.34  & 38.52    & 36.70   \\
\hline
  MLP     & 47.80 $\pm$ 0.51    & 318.29 $\pm$ 43.96 & 587.50 $\pm$ 51.50  & 56.75 $\pm$ 7.84  & 42.59 $\pm$ 3.73   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained using the CfsSubsetEval 
feature selection method (4 variables per book).}}
\label{tabla:results4}
\end{table*}

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_time.eps,width=11cm}
\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one). Plot shows that using categorical variables as part of the dataset makes the problem hard to solve. As expected, simpler methods are much faster to build the model than the complex ones.}}
\label{fig:time}
\end{center}
\end{figure}

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_rae.eps,width=11cm}
\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one). The M5P model obtains the lowest errors, whatever the dataset used.}}
\label{fig:rae}
\end{center}
\end{figure}

@@

%La investigación descrita en este trabajo se ha llevado a cabo conjuntamente con una empresa editorial que ha facilitado un conjunto de datos con los que trabajar, así como con la ayuda de un experto en ventas de este campo para validar los resultados obtenidos.
A data set consisting of 3159 books provided by the Spanish %FERGU: mover este párrafo debajo del siguiente
publishing company Trevenque Editorial has been used.

>>>>

%%%%%%%%%%%%%%%% Titulo %%%%%%%%%%%%%%%
\title{Enhancing the sales prediction of newly published books by means of computational intelligence methods}

% Antonio - El título habría que cambiarlo a otro más descriptivo, creo yo. A ver si os gusta este

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
\author {
P.A. Castillo, A.M. Mora, J.J. Merelo, P. Garc\'{\i}a-S\'anchez, \\ A.J. Fern\'andez-Ares, M.G. Arenas, P. de las Cuevas
}
\institute{Department of Computer Architecture and Computer Technology.\\
CITIC-ETSIIT. University of Granada (Spain) \\
           e-mail: {\tt pacv@ugr.es}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached shelves. 
Several years 
% Antonio - Decir cuántos años son, que no me acuerdo.
of data on published books in Spain have been processed by means of data visualization and other feature selection techniques. The aim is to find out what are the variables that have more impact on sales, and then use machine learning and forecasting methods to predict sales, and, from them, estimate the print-run.
The described methodology improves the forecasting running time and is eventually able to predict sales with remarkable accuracy. Moreover, the proposed method has been validated by the company that provided the data and incorporated in a business intelligence tool for publishers,
since the obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation.
% Antonio - esto es cierto??? :D
\end{abstract}

%********************************************************************************

\section{Introduction}

Publishing a book, as releasing any other product, implies several
types of risks and costs due to
the complexity and derived expenses of the production and distribution processes. 
% tienes que enmarcar el problema. Se trata de productos culturales
% con soporte físico y con ventas relativamente pequeñas. Libros,
% discos, no sé si alguna cosa más. - JJ
A newly launched product could be, additionally, completely new to the company (not a new version or edition of a previous product), and sales forecasts can
only be based on the experience of other similar products. 
In this scope, having accurate estimations of future sales of the new
product is extremely important \cite{ChingChin2010}, so that production
runs do not exceed predicted sales. 
Indeed, several studies have demonstrated that improving sale predictions 
(a reduction of forecasting errors) results in an enhancing in the 
production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

@@

Book publishers, as well as other content producers, release new {\em
  products} more frequently than other industries, so that they face the
problem of predicting sales quite often. The issue, in this case, is to print an
adequate number of copies but not too many, as the unsold volumes will
lead to losses and sunk inventory cost, 
% Antonio - 'sunk inventory cost' es corecto?
whereas if the number of printed copies was not enough, you can always print more. 
% Antonio - Esto habría que matizarlo más, de hecho, decirlo va un poco en contra de nuestro artículo, ya que simplifica el problema. Yo indicaría que errores en predicciones por exceso o por defecto tienen MUCHAS pegas (ambos casos), si bien el exceso es peor, claro, pero decir que lo otro es también muy negativo y por eso hay que ajustar muy bien la predicción. ;)
% Se podría señalar, por ejemplo:
% - repetición de costes de distribución
% - mala impresión al cliente/lector, que pueden repercutir negativamente en las ventas
% - algunas más... :D
In this sense, errors in one or the other direction do not have the same impact, although a temporal scarcity of a book that is selling well is also a problem.
% Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)

Thus, it is extremely important to develop an accurate predictive tool which could accurately forecast the future sales a new book will achieve, in order to optimize production and to improve the publishing company profits or minimize losses \cite{Zhao2001}. This is the main objective of this paper.
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. 
% Antonio - podrías extender un poco el ejemplo? Es decir, describir un poco más lo que se hace en ese trabajo. ;)

However, designing such an accurate predictive tool is a difficult task in this scope, as book sales are influenced by several factors that make them fluctuate and, moreover, usually they might be not controllable and even unknown. 
For instance, some are related with decisions on purchases, others with freight 
traffic, or others with the distribution strategy \cite{Little1998}.

Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager takes them into account \cite{Armstrong2001,SThomassey2014}. 
                                % ¿Esto también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ
                                % [Pedro] esto iba referido a la Industria Editorial.
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they do? What are the results?

In this research, the problem of how many units should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for book shops,
% Antonio - 'libraries' o 'book shops'? Supongo que lo segundo. ;D
publishers and distributors. 
Usually, the company's expert sales managers analyzed historical data 
and applied their knowledge using external variables to compute correct estimations (predictions), for instance, she can decide increasing or decreasing the sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.
%In any case, in general companies usually use a forecasting model and then, 
%an expert applies his knowledge, as the company might require an 
%interpretable and understandable model. 
However, carrying out the analysis and forecasting process as a human expert,
may lead to a 'fuzzy-like' analysis, which may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is quite large, and even, different experts can reach different
predictions from the same dataset \cite{ChingChin2010,Sanders1994}.

For these reasons, the industry requires the best suited forecasting
techniques to be adopted so that, estimating sales task is carried out
reliably, accurately, and in an automatic way.

With this issue in mind, in this paper a data visualization and preprocessing strategy to find out what are the relevant variables describing a book in the prediction of book sales is proposed; then several standard data mining models 
for sales forecasting are evaluated so a publishing company 
can deduce and optimize print-run.
% Antonio - cambiar este párrafo para describirlo como un proceso en dos pasos:
% - análisis y extracción
% - predicción

% Antonio - Además habría que justificar bien (con citas) el por qué de la extracción/selección de características, por ejemplo:
% - menor tiempo de procesamiento
% - mejores resultados (si algunas variables interfieren entre sí)

The rest of this paper is structured as follows: next, 
Section \ref{sec:soa} presents a comprehensive review of the
approaches found in the bibliography related to the prediction of
sales from product characteristics. 
Then, Section \ref{sec:problem} describes the 
problem of how many books should be printed when a new book is published, 
        % no es el problema de publicación, es el problema de venta
        % de libros sin publicar. Habrá que buscar un nombre - JJ
        %[Pedro] cierto, lo cambio, aunque me ha quedado un nombre muy largo  :)
 followed by Section \ref{sec:methodology} where the
experimental setup and the methodology considered in the study is
presented.  %FERGU: mejor described para no repetir
Section \ref{sec:experiments} reports and analyzes the obtained results with a 
real dataset. Finally, conclusions and future work are presented in Section
\ref{sec:conclusionsAndFutureWork}. 
% Antonio - TODO: rescribir con los contenidos finales del artículo. ;)

@@

The initial dataset, provided in the framework of a contract by
Trevenque Editorial, included 3159 books, and included descriptive information 
for each book, such as price, points of sale, subject, publisher, sales, returns, 
among other information.
Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
each book.

\begin{table}[!ht]
\caption{Parameters describing a book, as provided by the company Trevenque.}
\label{tabla:paramsOrig50}
\begin{center}
\begin{tabular}{|c|c|}
\hline

@@

\begin{figure}[!ht] 
\begin{center}
  \epsfig{file=stages.eps,width=7cm}
\caption{\small{Three main stages in a typical sales prediction process: data analysis, (2) forecasting 
methods testing, and (3) subjectively adjusting the obtained results.}}
\label{fig:stages}
\end{center}
\end{figure}

@@

 % weka.classifiers.functions.LinearRegression
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
 \item \emph{Linear Regression}:
 Linear regression \cite{Cohen2003,Yan2009,Rencher2102} method models the 
relationship between a scalar dependent variable (outcome) and several independent 
variables (predictor) over the range of values in the dataset. 
In this statistical technique, data is modeled using linear functions to estimate 
unknown model parameters, examining the linear correlations between independent 
and dependent variables.

@@

Once the methods to be applied have been chosen, they must be applied to datasets 
to obtain the prediction models for each one. 
Later on, the models ability must be validated on non-previously seen data.
Specifically, instead of using the conventional validation strategy based on 
using a training set and later on a testing set (unknown data against which 
the model must be tested), a cross-validation technique \cite{Geisser1993,Kohavi1995,Devijver1982} 
has been used to estimate how accurately the predictive model will perform in 
practice. %, limiting at the same time the overfitting problem.

@@

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
\begin{table*}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	      & MAE 		& RMSE 		& RAE (\%) & RRSE (\%) 		\\
\hline
  M5P 		& 24.24 $\pm$ 0.96    & 197.48  & 577.28  & 35.21    & 41.85  \\
\hline
  LR 		  & 3533.84 $\pm$ 178.38& 247.22 & 561.67  & 44.08    & 40.71    \\
\hline
  SVM 		& 5586.96 $\pm$ 139.71& 215.69  & 574.76  & 38.46    & 41.66  \\
\hline
  kNN 		& 0.02 $\pm$ 0.00     & 302.07 	& 924.94 	& 53.86 	 & 67.05 	\\
\hline
  MLP 		& - 	  & - 	& - 	& - 	& - 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the original dataset (16 variables per book). 
    In this case, due to the categorial variables, the MLP could not be run.}} 
\label{tabla:resultsT}
\end{table*}

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 7 variables per book (obtained 
using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
%In this dataset, every book is described using numerical variables, and thus, 
%processing the data to build the different models is a fast task.
%***************************************
% TODO: falta rellenar la tabla, una vez que hagamos el análisis con el SOM y decidamos qué variables incluir en este dataset
\begin{table*}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & 1.74 $\pm$ 0.10     & 218.81  & 661.85  & 39.01    & 47.98  \\
\hline
  LR      & 0.27 $\pm$ 0.02     & 258.82  & 582.74  & 46.15    & 42.24  \\
\hline
  SVM     & 45.58 $\pm$ 1.89    & 240.18  & 614.30  & 42.82    & 44.53  \\
\hline
  kNN     & 0.04 $\pm$ 0.00     & 221.21  & 520.17  & 39.44    & 37.71  \\
\hline
  MLP     & 8.99 $\pm$ 0.10   & 353.70 $\pm$ 57.74 & 624.87 $\pm$ 86.77  & 63.06 $\pm$ 10.29  & 45.30 $\pm$ 6.29   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained after the SOM analysis (7 variables per book).}}
\label{tabla:resultsSOM}
\end{table*}

@@

\begin{table*}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & 2.27 $\pm$ 0.02     & 195.97  & 629.33  & 34.94    & 45.62  \\
\hline
  LR      & 0.38 $\pm$ 0.01     & 256.19  & 549.19  & 45.68    & 39.81   \\
\hline
  SVM     & 132.64 $\pm$ 2.86   & 230.66  & 613.27  & 41.12    & 44.45   \\
\hline
  kNN     & 0.06 $\pm$ 0.01     & 214.76  & 551.33  & 38.29    & 39.96   \\
\hline
  MLP     & 130.77 $\pm$ 1.51   & 326.60 $\pm$ 75.77 & 687.61 $\pm$ 55.70  & 58.23 $\pm$ 13.51  & 49.84 $\pm$ 4.04   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained using the ReliefFAttributeEval 
feature selection method (8 variables per book).}}
\label{tabla:results9}
\end{table*}

@@

\begin{table*}[!ht]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 2.02 $\pm$ 0.01     & 205.52  & 556.90  & 36.64     & 40.37  \\
\hline
  LR      & 0.32 $\pm$ 0.00     & 261.04  & 547.42  & 46.54     & 39.68   \\
\hline
  SVM     & 81.74 $\pm$ 1.66    & 242.26  & 606.07   & 43.19    & 43.93   \\
\hline
  kNN     & 0.05 $\pm$ 0.00     & 216.05  & 506.34  & 38.52    & 36.70   \\
\hline
  MLP     & 47.80 $\pm$ 0.51    & 318.29 $\pm$ 43.96 & 587.50 $\pm$ 51.50  & 56.75 $\pm$ 7.84  & 42.59 $\pm$ 3.73   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained using the CfsSubsetEval 
feature selection method (4 variables per book).}}
\label{tabla:results4}
\end{table*}

\begin{figure}[!ht] 
\begin{center}
  \epsfig{file=fig_time.eps,width=11cm}
\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one). Plot shows that using categorical variables as part of the dataset makes the problem hard to solve. As expected, simpler methods are much faster to build the model than the complex ones.}}
\label{fig:time}
\end{center}
\end{figure}

\begin{figure}[!ht] 
\begin{center}
  \epsfig{file=fig_rae.eps,width=11cm}
\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one). The M5P model obtains the lowest errors, whatever the dataset used.}}
\label{fig:rae}
\end{center}
\end{figure}

@@

%La investigación descrita en este trabajo se ha llevado a cabo conjuntamente con una empresa editorial que ha facilitado un conjunto de datos con los que trabajar, así como con la ayuda de un experto en ventas de este campo para validar los resultados obtenidos.
A dataset consisting of 3159 books provided by the Spanish %FERGU: mover este párrafo debajo del siguiente
publishing company Trevenque Editorial has been used.
